% Chapter 1: Introduction and Motivation

\chapter{Introduction and Motivation}

Web applications routinely handle highly sensitive data through browser-based
forms, including identifiers, demographic attributes, financial records, and
medical information. In contemporary deployments, input validation is typically
performed by application backends or third-party services that receive raw
submissions, evaluate policy rules, and then accept or reject requests. This
centralization of validation logic implies that multiple parties see and often
store full user inputs, enlarging the attack surface and increasing the
consequences of compromise or misuse.

Zero-knowledge proof (ZKP) systems provide a way for a prover to convince a
verifier that an input satisfies a policy without revealing the input itself.
Recent advances have made succinct non-interactive arguments of knowledge
(SNARKs) practical for real-world systems, and toolchains such as Circom and
snarkjs allow developers to write and deploy constraint systems with relatively
low friction. Despite this progress, the use of ZKPs for classical web input
validation---rather than Web3 rollups or cryptocurrency protocols---remains
under-explored.

This monograph is driven by the following research question: \emph{Can a browser
outsource input validation to an untrusted service in such a way that the final
receiving system can verify correct validation without learning raw inputs?}
Addressing this question requires combining ideas from web security, applied
cryptography, and systems design.

To make this question concrete, we design and analyze PVE-ZKP (Proof-of-
Validated-Execution with zero-knowledge proofs), a system that introduces a
separate validation service into the form-submission path. The browser submits
form data to this validation service, which runs a set of zero-knowledge policy
checks, generates proofs, and returns only an opaque proof identifier to the
browser. The browser then forwards this identifier to the receiving system,
which fetches and verifies the corresponding proofs before deciding whether to
accept the submission. In this design, the receiving system bases its decision
solely on verified proofs and need not see raw form values.

PVE-ZKP is instantiated as a prototype for a healthcare-style registration form
using Circom for circuit definitions and Node.js for both the validation
service and the receiving system. The prototype is intentionally modest in
scope: it implements five reusable policy circuits, a single trusted-setup
workflow, and a browser-based demo application. The goal of this monograph is
not to present a finished product, but to document a research system that can
serve as a foundation for later conference papers and a full thesis.

The remainder of this document expands on and generalizes the shorter
conference-style paper. It provides additional background, formalizes the
problem and system model, explains the PVE-ZKP architecture in detail, walks
through circuit and implementation design choices, and offers a more extensive
security analysis and discussion of limitations and future work.
