% Chapter 3: Problem Statement and System Model

\chapter{Problem Statement and System Model}

This chapter formalizes the input-validation problem addressed by PVE-ZKP. It
introduces the participating entities, the data to be protected, the goals and
non-goals of the system, and the threat assumptions under which the design is
intended to operate.

\section{Problem Statement}

Consider a web application that accepts submissions from users via
browser-based forms. The application must decide whether to accept or reject
each submission according to a set of validation policies, such as:

\begin{itemize}[leftmargin=*]
  \item format and structural constraints on strings (e.g., postcodes);
  \item range constraints on numeric values (e.g., age thresholds);
  \item membership in an approved set (e.g., roles or countries);
  \item integrity of hidden fields bound to server-side state; and
  \item restrictions on path-like strings used for file uploads or URLs.
\end{itemize}

In conventional architectures, the application backend evaluates these policies
using the raw form data. If an external validation service is used, the backend
sends the raw data to the validator, which returns a decision. In both cases,
multiple parties see sensitive inputs.

The core problem we study is how to enable the application backend (the
receiving system) to validate submissions according to specified policies
\emph{without} needing to see the raw inputs, and without having to fully trust
a separate validation service.

\section{Entities and Data Flows}

PVE-ZKP models three logical components:

\begin{itemize}[leftmargin=*]
  \item \textbf{Browser client:} runs in the user's environment and displays
the form. It collects form fields, sends them to the validation service, and
later forwards a proof identifier to the receiving system.
  \item \textbf{Validation service:} an external or third-party service that
receives raw form data, runs zero-knowledge policy checks, generates proofs,
and stores them under an opaque identifier.
  \item \textbf{Receiving system:} the application backend that ultimately
accepts or rejects submissions based on verified proofs obtained from the
validation service.
\end{itemize}

The high-level data flow is:

\begin{enumerate}[leftmargin=*]
  \item The browser sends form data to the validation service.
  \item The validation service runs policy circuits and stores resulting proofs
        under a short identifier, \texttt{proofId}.
  \item The browser sends only \texttt{proofId} (and optional non-sensitive
        metadata) to the receiving system.
  \item The receiving system fetches proofs using \texttt{proofId}, verifies
        them, and then accepts or rejects the submission.
\end{enumerate}

\section{Goals and Non-Goals}

The design goals of PVE-ZKP can be summarized as:

\begin{itemize}[leftmargin=*]
  \item \textbf{G1 (Data minimization):} the receiving system should not require
    access to raw form inputs in order to enforce validation policies.
  \item \textbf{G2 (Trust separation):} the receiving system should not have to
    fully trust the validation service; instead, it should rely on verifiable
    zero-knowledge proofs.
  \item \textbf{G3 (Policy expressiveness):} common input validation patterns
    should be expressible as Circom circuits without excessive complexity.
  \item \textbf{G4 (Deployability):} the architecture should integrate with
    existing web technologies and development practices.
\end{itemize}

Non-goals include providing formal end-to-end privacy guarantees in the
presence of arbitrary application-layer logic, replacing all forms of server-
side validation, or optimizing proof generation for very large-scale,
latency-sensitive deployments. These topics are discussed further as future
work.

\section{Threat Assumptions}

PVE-ZKP assumes standard network adversaries who may eavesdrop on or attempt to
modify traffic outside of transport-layer security, as well as application-
layer adversaries who may control the browser client or try to exploit the
validation service. The receiving system is assumed to follow its verification
logic but may be operated by a different organization than the validator.

The adversary may:

\begin{itemize}[leftmargin=*]
  \item tamper with client-side scripts or send arbitrary HTTP requests;
  \item attempt to trick the validator into generating proofs for invalid
        inputs;
  \item attempt to replay previously issued proofs; or
  \item attempt to correlate proof identifiers and timing information to infer
        information about inputs.
\end{itemize}

Subsequent chapters analyze how PVE-ZKP's architecture and policy circuits
address these threats, and where additional mechanisms are needed.
