% Chapter 6: Implementation

\chapter{Implementation}

This chapter explains how the PVE-ZKP architecture and policy circuits are
implemented in the open-source prototype. It describes the directory structure,
key scripts and services, and the end-to-end workflow for building circuits,
generating proofs, and verifying them.

\section{Project Structure}

The prototype repository is organized as follows:

\begin{verbatim}
pve-zkp/
├── circuits/           Circom constraint files (5 circuits)
├── prover/
│   ├── generate_proof.js   CLI proof generator
│   ├── validator.js        Express validation service (:3001)
│   └── inputs/             Sample JSON inputs for each circuit
├── verifier/
│   ├── verify_proof.js         CLI proof verifier
│   └── receiving_system.js     Express receiving system (:3002)
├── webapp/
│   ├── index.html          Healthcare registration form
│   └── submit.js           Client-side ZKP submission handler
├── keys/               Generated keys (after build)
├── outputs/            Generated proofs (after prove)
├── scripts/
│   ├── build_circuits.sh   Full build pipeline
│   └── test_e2e.sh         End-to-end test runner
└── package.json
\end{verbatim}

This layout mirrors the logical separation between circuits, proving logic,
verification logic, and the web front end.

\section{Circuit Build and Trusted Setup}

The \texttt{scripts/build\_circuits.sh} script orchestrates compilation and
trusted setup for all policy circuits. It downloads a powers-of-tau file,
compiles the Circom source files into R1CS and WebAssembly artifacts, runs the
Groth16 setup phase for each circuit, and exports verification keys into the
\texttt{keys/} directory.

The trusted setup in the prototype is single-party and suitable only for
experimentation. A production deployment would require a multi-party ceremony
to avoid reliance on a single setup participant.

\section{Validation Service Implementation}

The validation service, implemented in \texttt{prover/validator.js}, is an
Express application that exposes two main endpoints:

\begin{itemize}[leftmargin=*]
  \item \texttt{POST /validate}: accepts JSON-encoded form data, runs all five
    policy circuits using snarkjs to generate Groth16 proofs, and stores the
    resulting proofs in an in-memory map keyed by a random \texttt{proofId}.
  \item \texttt{GET /proof/:id}: returns the stored proofs and public signals
    for the given identifier, without exposing raw inputs.
\end{itemize}

Helper functions handle string-to-ASCII conversion, age computation from a date
of birth, and construction of circuit inputs. Environment variables configure
values such as server-side secrets.

\section{Receiving System Implementation}

The receiving system, implemented in \texttt{verifier/receiving\_system.js}, is
another Express application. It exposes a single main endpoint:

\begin{itemize}[leftmargin=*]
  \item \texttt{POST /receive}: accepts a JSON body containing \texttt{proofId},
    fetches proofs from the validation service, loads verification keys for each
    circuit from \texttt{keys/}, and verifies all proofs using snarkjs. It
    returns an accept/reject decision and a reason on failure.
\end{itemize}

The receiving system never processes raw form inputs. Its logic is entirely
expressed in terms of proof verification.

\section{Browser Application}

The browser-facing part of the prototype resides in the \texttt{webapp/}
folder. The main HTML page contains a healthcare-style registration form, and
\texttt{submit.js} attaches a handler that:

\begin{enumerate}[leftmargin=*]
  \item collects form values and sends them to the validation service at
        \texttt{/validate};
  \item receives a \texttt{proofId} on success; and
  \item sends a follow-up request containing only \texttt{proofId} to the
        receiving system at \texttt{/receive}.
\end{enumerate}

Client-side checks provide immediate feedback but are treated as a usability
feature, not a security boundary.

\section{End-to-End Workflow}

To run the prototype end to end, a developer installs dependencies, builds the
circuits, starts the validation and receiving services, and opens the browser
form. A helper script runs end-to-end tests that exercise all five policy
circuits against sample inputs.

This implementation chapter ties the abstract architecture to concrete code and
scripts, which in turn support the security analysis and limitations discussed
in subsequent chapters.
