% Chapter 8: Limitations and Future Work

\chapter{Limitations and Future Work}

This chapter expands on the limitations of the current PVE-ZKP system and
outlines directions for future research and engineering work. The goal is to
clarify what the present design does \emph{not} provide and to sketch a roadmap
for strengthening and extending it.

\section{Trusted Setup}

The prototype relies on a single-party trusted setup for each Groth16 circuit.
This is acceptable for experimentation but undesirable in production, as a
setup participant who retains trapdoor information could, in principle,
construct fraudulent proofs.

Future work should replace the single-party setup with a multi-party
computation (MPC) ceremony, ideally using existing tooling and best practices
from other SNARK deployments. The thesis treats the setup as a modular
component that can be swapped without changing the architecture.

\section{Proof Storage and Durability}

Proofs are currently stored in an in-memory map inside the validation service.
This design is simple but has several drawbacks: proofs are lost on service
restart, no explicit retention policy is enforced, and there is no access
control beyond the service's own process boundary.

A more robust design would use a dedicated data store such as a database or
cache with strict access control, audit logging, and time-to-live policies.
This would also support horizontal scaling and fault tolerance for the
validation service.

\section{Performance and Scalability}

The current implementation does not yet include empirical benchmarks for
proof-generation time, verification time, or resource consumption. These
measurements are essential for understanding how PVE-ZKP behaves under
realistic loads and for identifying bottlenecks.

Future work should design and run experiments that measure performance for
various circuit sizes, concurrency levels, and deployment settings. The
evaluation chapter outlines a methodology for such experiments and indicates
how results could influence circuit design, parameter choices, and deployment
recommendations.

\section{Side-Channel Leakage}

Timing differences, error messages, and network-level patterns may reveal
information about inputs beyond what is captured in the zero-knowledge proofs
themselves. The current implementation does not attempt to equalize computation
time or randomize responses to mitigate such side channels.

Investigating the impact of side-channel leakage in this architecture, and
exploring mitigations such as constant-time implementations or rate limiting,
is an important direction for future work.

\section{Policy Coverage and Expressiveness}

The five policy circuits implemented in PVE-ZKP cover only a subset of
validation patterns that arise in real applications. They do not, for example,
handle complex cross-field dependencies, multi-step workflows, or adaptive
policies based on external data.

Extending the policy library to support richer constraints, while keeping
circuits auditable and efficient, is an open design challenge. Additional work
is needed to develop higher-level abstractions for composing policy circuits
and for verifying that combined policies behave as intended.

\section{Broader Research Directions}

Beyond immediate engineering improvements, several broader research directions
emerge from this thesis. These include integrating circuit-analysis tools into
the development workflow, exploring combinations of ZK-based validation with
other privacy-enhancing technologies, and adapting the architecture to
multi-tenant and distributed settings.
