% Chapter 9: Conclusion

\chapter{Conclusion}

This monograph has presented PVE-ZKP, a system that applies zero-knowledge
proofs to the problem of input validation for browser-based forms. By
introducing a dedicated validation service that runs policy circuits over raw
inputs and returns only proof identifiers to the browser, PVE-ZKP enables the
receiving system to base its acceptance decisions on verifiable proofs rather
than on a position of blind trust.

The work is motivated by the need to reduce unnecessary exposure of sensitive
user data and to separate the concerns of policy enforcement and data storage.
Using Circom and snarkjs, PVE-ZKP implements a concrete architecture with five
policy circuits and demonstrates that such an approach can be integrated into
familiar web workflows without major changes to the browser or backend stacks.

Beyond describing the prototype, the monograph has provided background on
zero-knowledge proofs, formalized the system model and threat assumptions,
explained the architecture and circuit design, and analyzed security
properties, limitations, and future directions. The prototype has clear
limitations, but it serves as a basis for further exploration of privacy-
preserving input validation and for more formal research contributions.

In the near term, PVE-ZKP can be extended with stronger trusted-setup
mechanisms, more robust proof storage, richer policy circuits, and empirical
evaluations. In the longer term, the ideas developed here can inform conference
papers and a full thesis that explore the broader design space of verifiable and
privacy-preserving validation services in web and distributed systems.
